### 2012-05-11 Rctl/inst/doc/manual.Rnw
[Rctl] manual updates

After you have stored the data as plain text open the files in a text editor (NOT WORD, for 
windows Notepad++ is a good option) and check to see if your data is stored correctly, if 
not reformat your data in both the genotype.csv and the phenotype.csv files to match the 
format below.
{\color{red} \emph{\bf{ \\\\NOTE: Individual order must match between the genotype and the phenotype file... \\\\}}} 
The phenotypes.csv file containing the genotype matrix is stored individuals x genetic marker:

@@

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:51 were in condition A / e.g. treatment A
#Specify that individuals 52:100 were in condition B / e.g. treatment B 
#Specify that individuals 101:162 were in condition C / e.g. control
conditions <- c(rep(1,51),rep(2,49),rep(2,62))
ctls <- CTLscan(geno, traits, conditions=conditions)
@

>>>>

After you have stored the data as plain text open the files in a text editor (NOT WORD, for 
windows Notepad++ is a good option) and check to see if your data is stored correctly, if 
not reformat your data in both the genotype.csv and the phenotype.csv files to match the 
format below.
{\color{red} \emph{\bf{ \\\\NOTE: Individual order must match between the genotype and the phenotype file... \\\\}}} 
The genotypes.csv file containing the genotype matrix is stored individuals x genetic marker:

@@

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:51 were in condition A / e.g. treatment A
#Specify that individuals 52:100 were in condition B / e.g. treatment B 
#Specify that individuals 101:162 were in condition C / e.g. control
conditions <- c(rep(1,51),rep(2,49),rep(3,62))
ctls <- CTLscan(geno, traits, conditions=conditions)
@
